The \dealii Library, Version 9.1

### 2019-06-10 9.1/paper.tex
Add a couple of sentances on what the uses of a CAS are.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dedicated support for symbolic algebra, including algebra differentiation}
\label{subsec:sd}
To complement the automatic differentiation features in \dealii{}, this release sees
the first step towards integrating and supporting a highly performant computer algebra
system (CAS) via the SymEngine library \cite{symengine-web-page}.
The \texttt{Expression} class in the namespace \texttt{Differentiation::SD} interfaces
to SymEngine and forms the basis of symbolic computations, offering a full set of
overloaded operators and a C++ style interface. This class offers the following
basic functionality:
\begin{itemize}
\item symbolic variable definition,
\item symbolic function definition,
\item expression creation using standard C++ syntax,
\item expression parsing,
\item comparison operations,
\item logical operations,
\item conditional expression construction,
\item differentiation,
\item substitution (partial and complete), and
\item serialization.
\end{itemize}
\dealii{} now also provides an extensive set of math operations, with a syntax mimicking that used
in the C++ standard library. Using the \texttt{Expression} class as a basis, we
have developed a set of functions that can be used to create \dealii{} \texttt{Tensor}s
and \texttt{SymmetricTensor}s of symbolic variables and symbolic functions. This
gives full symbolic tensor algebra support using the pre-existing \texttt{Tensor}
and \texttt{SymmetricTensor} classes and associated functions. We have
also implemented a set of utility functions with the following features:
\begin{itemize}
\item \texttt{differentiate} scalar, tensor, and symmetric tensor expressions
with respect to other scalar, tensor, or symmetric tensor expressions;
\item create symbolic substitution maps;
\item resolve explicit dependencies between expressions; and
\item perform scalar and tensor valued substitution (including conversion from symbolic to
real-valued scalars and tensors).
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dedicated support for symbolic algebra, including algebra differentiation}
\label{subsec:sd}
To complement the automatic differentiation features in \dealii{}, this release sees
the first step towards integrating and supporting a highly performant computer algebra
system (CAS) via the SymEngine library \cite{symengine-web-page}.
This allows the development of exact algebraic expressions using variables that are
manipulated symbolically and may represent any value (or supported data structure).
In the context of finite element simulations, typical applications include (but, due to
the generality of the CAS, are not limited to) the development of constitutive models
and the implementation of finite element assembly operations through the construction
and linearization of finite element residuals.

The \texttt{Expression} class in the namespace \texttt{Differentiation::SD} interfaces
to SymEngine and forms the basis of symbolic computations, offering a full set of
overloaded operators and a C++ style interface. This class offers the following
basic functionality:
\begin{itemize}
\item symbolic variable definition,
\item symbolic function definition,
\item expression creation using standard C++ syntax,
\item expression parsing,
\item comparison operations,
\item logical operations,
\item conditional expression construction,
\item differentiation,
\item substitution (partial and complete), and
\item serialization.
\end{itemize}
\dealii{} now also provides an extensive set of math operations, with a syntax mimicking that used
in the C++ standard library. Using the \texttt{Expression} class as a basis, we
have developed a set of functions that can be used to create \dealii{} \texttt{Tensor}s
and \texttt{SymmetricTensor}s of symbolic variables and symbolic functions. This
gives full symbolic tensor algebra support using the pre-existing \texttt{Tensor}
and \texttt{SymmetricTensor} classes and associated functions. We have
also implemented a set of utility functions with the following features:
\begin{itemize}
\item \texttt{differentiate} scalar, tensor, and symmetric tensor expressions
with respect to other scalar, tensor, or symmetric tensor expressions;
\item create symbolic substitution maps;
\item resolve explicit dependencies between expressions; and
\item perform scalar and tensor valued substitution (including conversion from symbolic to
real-valued scalars and tensors).
\end{itemize}
